---
title: "Cabbages"
author: "Daniela Olvera-Mota"
date: "Fall 2023"
output:
  html_document:
    df_print: paged
---

```{r include=FALSE,echo=FALSE}
require(tidyverse)
require(tigerstats)
require(MASS)
# Load necessary libraries
library(ggplot2)
library(dplyr)

veggy <- cabbages
```

# Introduction

<!--In this section you explain what you are trying to show.  Where did the data come from?  What is the research or other question you are trying to answer?!-->
 The cabbages data from the MASS package is loaded into a dataframe called veggy. Complete this report by answering the following two questions  
 
### Is there a difference in average VitC between c39 and c52 cultivation methods?

$H_0$:There is no difference in the vitamin C content of cabbages based on cultivation method.

$H_A$:There is a difference in the vitamin C content of cabbages based on cultivation method.

# Methods

<!--Decide on your methods:  use "variable analysis" or other appropriate descriptors.  Make sure to choose at least one graphical method and at least one numerical method.!-->

Vitamin C content is a numerical variable , cultivation method is a categorical variable.

```{r}
data=veggy
```


# Results

<!--Divide this section into two sub-sections:  One for your descriptive  results and one for your inferential results.!-->

## Descriptive Results

### Graphical Descriptive Results

```{r}
# create a box plot
ggplot(data, aes(x = Cult, y = VitC)) +
  geom_boxplot() +
  labs(x = "Cult", y = "VitC")
```

This boxplot shows the VitC of c39 and c52.c52 has a greater amount of Vitc than c39 by about 13-14 more units of VitC.

<!--Graphical results here.  Make sure to show your code.  Provide appropriate labels for axes, giving units if possible, and provide a good title for the graph, too.  Use the graphical results to describe the patterns if any that exist in the data as focused toward the research question!-->

### Numerical Descriptive Results

```{r}
# Calculate summary statistics
summary_stats <- data %>%
  group_by (Cult) %>%
  summarise(
    Mean = mean(VitC),
    Median = median(VitC),
    SD = sd(VitC),
  )

summary_stats
```

This table shows that the median of VitC for c39 is 51.0 and the median for VitC of c52 is 64.5.


<!--Numerical results go here. Use the numerical results to describe the patterns if any that exist in the data as focused toward the research question!-->

## Inferential Results

```{r}
t.test(VitC~Cult,data=veggy)
```
The p value is less than 0.05 so we reject the null hypothesis.


<!--State hypothesis clearly.  Make sure your discussion of the inferential test covers all the aspects that the test output produces, such as test statistic, p-value etc.  Make a decision about the null hypothesis, explain the assumptions on which the selected test/procedure was based, and why the chosen procedure satisfys the assumptions and is appropriate to answer the research question!-->




# Discussion and Conclusion

The p value is 0.00000003405. The p value is smaller than 0.5 so we would reject it. We reject the null hypothesis that there is no difference. Instead we know that there is a difference 


<!--Discussion and conclusion here.  If you found a relationship be sure to consider whether the relationship occurs because one of the variavbles causes the other, or whether they perhasps are related for some other reason.  Watch the chapter 6 videos from the GeorgeTown videos collection.!-->
